---
title: "Fitbit R"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fitbitr)
library(tidyverse)
library(lubridate)
library(httr)
library(kableExtra)
library(chron)
library(tsibble)
library(tsibbledata)
library(fabletools)
library(feasts)
source("get_heart_rate_intraday_time_series_multiple.R")
```

## Get your own Fitbit data

First step is to download your own data from Fitbit using `fitbitr` package (available at github: `devtools::install_github("teramonagi/fitbitr")`). You will need to get your own token (see instructions ~[here](https://github.com/teramonagi/fitbitr)) and then you will be using  your own FITBIT_KEY and FITBIT_SECRET.

```{r}
FITBIT_KEY    <- ""
FITBIT_SECRET <- ""
FITBIT_CALLBACK <- "http://localhost:1410/"

token <- fitbitr::oauth_token(language = "en_US")
#saveRDS(token, file = "fitbit_token.rds")
#token <- readRDS("fitbit_token.rds")
```

### Whole day heart rate

Let's asume we want to start with downloading your whole day heart rate for first 10 days for January:

```{r}
df_hr <- get_heart_rate_intraday_time_series_multiple(token = token, date_start = "2020-01-05", date_end = "2020-01-10")
df_hr$time <- times(df_hr$time)
```

Convert to tsibble:

```{r}
df_hr$date_time <- as.POSIXct(paste(df_hr$day, df_hr$time), format = "%Y-%m-%d %H:%M:%S")
tdf <- tsibble(df_hr %>% select(date_time, value) %>% mutate(id = 1),
               key = id,
               index = date_time)
tdf %>% fabletools::autoplot(value)
```

Let's now plot the heart rate:

```{r}
tdf %>% tsibble::fill_gaps() %>% feasts::gg_season(value, period = "day")
```

# Resting heart rate (RHR)

Now let's look at resting heart rate:

```{r}
rhr <- get_activity_time_series(token, "restingHeartRate", date = as.character(Sys.Date()), period = "max")
rhr$date <- as.Date(rhr$dateTime)
rhr$value <- as.numeric(rhr$value)
ggplot(rhr, aes(x = date, y = value)) +
  geom_line(col = "gray") +
  stat_smooth(aes(x = date, y = value), method = "lm", formula = y ~ poly(x, 25), se = FALSE) +
  theme_mine() + 
  ylab("RHR") + 
  xlab("") +
  scale_x_date(date_breaks = "1 month", date_labels = "%b '%y")
```

Convert to tsibble:

```{r}
rhr_ts <- tsibble(rhr %>% select(date, value) %>% mutate(id = 1),
               key = id,
               index = date)
rhr_ts %>% fabletools::autoplot(value)
```

Plot and look at autocorrelation

```{r}
rhr_ts %>% tsibble::fill_gaps() %>% feasts::gg_season(value, period = "month")
```

```{r}
rhr_ts %>% tsibble::fill_gaps() %>% ACF(rhr_ts, lag_max = 31) %>% 
  autoplot()
```

```{r}
rhr_ts %>% gg_lag(value, geom = "point", lags = c(20:30))
```


